### 2014-06-11 paper/paper.tex
revision 1 submitted

Two main goals can be identified in this paper: first, the proposed algorithm must be applicable to real-time domains (those where the next move to make must be decided within a small time budget) and it should obtain better or at least the same performance than the other state-of-the-art algorithms. It is important to highlight that all three algorithms tested employ the same heuristic functions to evaluate the features of a given game state. Thus, the focus of this research is set on how the algorithm explores the search space, instead of providing the best possible solution to each given problem.

@@

The three main pillars of the NSGA-II algorithm are:
\begin{itemize}
\item Fast non-dominated sorting: The function $F = \Call{fastNonDominatedSort}{U(t)}$ performs a non-dominated sorting and ranks the individuals stored in a set $U$ into several non-dominated fronts denoted as $F_i$, where the solutions in $F_0$ are the non-dominated solutions in the entire set. $F_i$ is the set of non-dominated solutions in $R \setminus (F_0 \cup \cdots \cup F_{i-1})$. 
\item Crowding distance: The function $\Call{crowdingDistanceAssignment}{F_i}$ assigns to each one of the individuals in $F_i$ a crowding distance value, which is the distance between the individual and its neighbours. The individuals with the smallest crowding distances are selected with a lower probability than the ones with larger values.   
\item Elitism: The individuals from the first front $F_0$ are always ranked first, according to the dominance criterion and their crowding distance. This ensures that the best solutions always survive to the next generation.
\end{itemize}

@@

Finally, in the comparison between NSGA-II and MO-MCTS, the latter algorithm obtains higher percentages for each one of the points in the front. This result suggests that, with a limited number of iterations/evaluations, the proposed algorithm is able to explore the search space more efficiently than a rolling horizon version of a state-of-the-art NSGA-II.

>>>>

Two main goals can be identified in this paper: first, the proposed algorithm must be applicable to real-time domains (those where the next move to make must be decided within a small time budget) and it should obtain better or at least the same performance than the other algorithms. It is important to highlight that all three algorithms tested employ the same heuristic functions to evaluate the features of a given game state. Thus, the focus of this research is set on how the algorithm explores the search space, instead of providing the best possible solution to each given problem.

@@

The three main pillars of the NSGA-II algorithm are:
\begin{itemize}
\item Fast non-dominated sorting: The function $F = \Call{fastNonDominatedSort}{U(t)}$ performs a non-dominated sorting and ranks the individuals stored in a set $U$ into several non-dominated fronts denoted as $F_i$, where the solutions in $F_0$ are the non-dominated solutions in the entire set. $F_i$ is the set of non-dominated solutions in $R \setminus (F_0 \cup \cdots \cup F_{i-1})$. 
\item Crowding distance: The function $\Call{crowdingDistanceAssignment}{F_i}$ assigns to each one of the individuals in $F_i$ a crowding distance value, which is the distance between the individual and its neighbours. The individuals with the smallest crowding distances are selected with a lower probability than the ones with larger values.   
\item Elitism: The individuals from the first front $F_0$ are always ranked first, according to the dominance criterion and their crowding distance. 
\end{itemize}

@@

Finally, in the comparison between NSGA-II and MO-MCTS, the latter algorithm obtains higher percentages for each one of the points in the front. This result suggests that, with a limited number of iterations/evaluations, the proposed algorithm is able to explore the search space more efficiently than a rolling horizon version of NSGA-II.
